### 2018-08-06 Writeup/PERT_New.tex
Update the extensive formulation

		(M) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega(t,x)\\

@@

		(S_P^\omega) \qquad \min \quad & t_T \\

@@

	Suppose we solve the subproblems \((S_P^\omega)\) for every \(\omega \in \Omega\) and generate a linear cut indexed by \(\ell\):

@@

		\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).

@@

		& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber\\

@@

@@

		(M_P) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\

@@

		&\qquad + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber \\

@@

	\textcolor{blue}{
		\item algorithm
		\item end points of each partition
		\item proof of convergence if we have \(y_i^q\) for every \(\omega\)
	\end{itemize}}
	\textcolor{blue}{ The materials above are the most important idea I want to convey in this section. Here are some additional results we have discussed but I haven't compiled to \LaTeX \ yet. Time allowing, I can add some stuff in maybe tonight or this coming week.
			\item Concavity of \(\mathbb{E}_d \left[ f(x,H,d) | H \right]\) in \(d\).
			\item The analytical form of the recourse function when all \(d\) are \([0,1]\)-uniformly distributed, all \(D\) are equal, and the crashing option can only be integer.
			\item The recourse function is a decreasing function in terms of remaining budget, given the same remaining task set.
			\item Not optimal to delay the start of activity \(i\) unless there is no investment before \(i\), given a fixed \(H\).
			\item Only optimal to delay to a possible disruption time.
	}
	\subsection{Parallel Networks}
			\item Not optimal to delay when \(d_i \geq 0\) if each branch only contains a single activity.
			\item If each branch is a serial path, it is possibly beneficial to delay the start of some activities.
	\subsection{Y Networks}
\section{Properties of the Sample Average Approximation Problem} \label{sec:consistency}
	\subsection{Cheat?}
	\subsection{Consistency and Convergence Results}
	\subsection{IID vs. Stratified Sampling}

>>>>

		(M) \quad z^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega(t,x)\\

@@

		(S_P^\omega) \qquad v^\omega = \min \quad & t_T \\

@@

	Suppose we solve the subproblems \((S_P^\omega)\) for every \(\omega \in \Omega\) and generate a linear cut indexed by \(\ell\), where coefficients \(\pi,\lambda\) and \(\gamma\) can be calculated based on the dual variables obtained:

@@

		\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).

@@

		& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, H^{\bar{\omega}^{\tilde{q}}} \leq H^{\bar{\omega}^{q,\ell}},H^{\underbar{\omega}^{\tilde{q}}} \geq H^{\bar{\omega}^{q,\ell}} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber\\

@@

	\begin{subequations} \label{prob:masterTightened}

@@

		(M_P) \quad z_P^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\

@@

		&\qquad + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber \\

@@

	The decomposition algorithm is presented as follows:
	\begin{algorithm}
		\caption{Decomposition algorithm for model~\eqref{prob:extensive}}
		\label{alg:Cut}
		\begin{algorithmic}[1]
			\State Initialize with cut iteration number \(\ell := 0\), lower bound \(LB := 0\), upper bound \(UB := +\infty\), initial partition \(\mathcal{P}^\ell\) with its indexed set \(\mathcal{Q}^\ell\), and specified tolerance \(\epsilon > 0\) and \(\delta > 0\);
			\While{\(\frac{UB - LB}{UB} > \epsilon\)} 
			\State Solve master problem \((M_P)\) and obtain solution \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and optimal value \(z_{P}^*\);
			\State Update \(LB = z_{P}^*\) if \(z_{P}^* > LB\);
			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t},\hat{x})\). 
			\State Calculate \(z^* = p^0 \hat{t}_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t},\hat{x})\) and update \(UB := z^*\) if \(z^* < UB\);
			\State For each \(\omega \in \Omega\), solve problem \((S_P^\omega)\) given \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and obtain optimal value \(v^{\omega,\ell}\) and coefficients \(\pi^{\omega,\ell}, \lambda^{\omega,\ell}, \gamma^{\omega,\ell}\);
			\If{\(z^*_P \geq p^0 \hat{t}_T + \sum_{\omega \in \Omega} p^\omega v^{\omega,\ell} - \delta\)}
			\State Obtain optimal value \(V^*\); 
			\Else
			\State Stop and return the status of infeasibility;
			\EndIf
			\vspace{0.1cm}
			\EndWhile{\textbf{end while}}
			\State Output \(V^*\) as a lower bound on the optimal value of model~\eqref{prob:extensive}, and output \(\hat{s}^{p,k}, \hat{s}^{q,k}\) as an \(\epsilon\)-feasible solution.
		\end{algorithmic}
	\end{algorithm}

	\textcolor{blue}{
	\begin{itemize}
		\item algorithm
		\item end points of each partition
		\item proof of convergence if we have \(y_i^q\) for every \(\omega\)
	\end{itemize}}
	\begin{comment}
	\textcolor{blue}{ The materials above are the most important idea I want to convey in this section. Here are some additional results we have discussed but I haven't compiled to \LaTeX \ yet. Time allowing, I can add some stuff in maybe tonight or this coming week.
		\begin{itemize}
			\item Concavity of \(\mathbb{E}_d \left[ f(x,H,d) | H \right]\) in \(d\).
			\item The analytical form of the recourse function when all \(d\) are \([0,1]\)-uniformly distributed, all \(D\) are equal, and the crashing option can only be integer.
			\item The recourse function is a decreasing function in terms of remaining budget, given the same remaining task set.
			\item Not optimal to delay the start of activity \(i\) unless there is no investment before \(i\), given a fixed \(H\).
			\item Only optimal to delay to a possible disruption time.
		\end{itemize}
	}
	\subsection{Parallel Networks}
		\begin{itemize}
			\item Not optimal to delay when \(d_i \geq 0\) if each branch only contains a single activity.
			\item If each branch is a serial path, it is possibly beneficial to delay the start of some activities.
		\end{itemize}
	\subsection{Y Networks}
\section{Properties of the Sample Average Approximation Problem} \label{sec:consistency}
	\subsection{Cheat?}
	\subsection{Consistency and Convergence Results}
	\subsection{IID vs. Stratified Sampling}
